Converging High-Throughput and High-Performance Computing Paradigms: \\ A Case Study of Using Abstractions to Bridge the Divide

### 2017-03-12 overall.tex
Address #3

Figure~\ref{fig:hpc-workload-utilization} shows that between January 2016 and
February 2017, about 2.25M million detector simulation jobs were completed on
Titan, for a total of 225M events processed. This is equivalent to 9\% of all
the 250M detector simulations performed by ATLAS in the same period of time, and
3.5\% of the 6.6B events processed by those jobs. Comparatively, Titan
contributed 3.9\% of the total of around 200K cores available to ATLAS on Grid,
Cloud, and HPC infrastructures together. These figures confirms the relevance of
supercomputers' resource contribution to the LHC Run 3, especially when
accounting for the amount of unused backfill availability and the rate of
improvement of PanDA efficiency.

>>>>

Figure~\ref{fig:hpc-workload-utilization} shows that between January 2016 and
February 2017, about 2.25M detector simulation jobs were completed on Titan, for
a total of 225M events processed. This is equivalent to 0.9\% of all the 250M
detector simulations performed by ATLAS in the same period of time, and 3.5\% of
the 6.6B events processed by those jobs. Comparatively, Titan contributed 3.9\%
of the total of around 200K cores available to ATLAS on Grid, Cloud, and HPC
infrastructures together. These figures confirms the relevance of
supercomputers' resource contribution to the LHC Run 3, especially when
accounting for the amount of unused backfill availability and the rate of
improvement of PanDA efficiency.
